---
title: "HW dates selection"
author: "E. Di Giuseppe"
date: "19 maggio 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  IDENTIFICATION OF HEAT WAVES DATES AT LARGE SPATIAL DOMAIN      

1) starts from `t?_ECAD_Duration_HeatWave_Cut1_Extended_Marginal.nc files;
2) identifies the whole relative maximum and their dates;
3) creates output files (ASCII and NetCDF)
*******
The data listed below can be loaded into R from the following file:

```{r List,include=FALSE}
library(ncdf4)
library(zoo)
```
```{r  RData}
load("HW_SpatialExtension.RData")
ls()
```

The objects `tn_Area1_final` and `tx_Area1_final` have been also created both as *.txt* and *.nc* files. These files are loaded in the [GitHub repository](https://github.com/edidigiu/MedHW.git).


The  `tn_Area1_final` and `tx_Area1_final` are multiple time series. The table below is an example of HW events selection for **tn**:

```{r Data Explanation,echo=FALSE}
tn_Area1_final[19140:19200]
```

where the column `x` represents the number of cells in the domain area (Central-Western Mediterranean basin) which have been hit by an HW; the column `x7` is built searching iteratively the maximum number of cells once the nearest $7$ time points $(-7days; +7days)$ are set to $0$; and the column `x10` is similar to `x7` except for the time window which is $(-10days; +10days)$.

The results of setting different time windows is reported in the following tables, where the reported **HW events** are also tabulated according to classes of cells number involved in each event:

```{r TableFinal}
tn_Area1_tab
tx_Area1_tab
```


The same tables for the period May-September are reported below:

```{r TableFinalMaySept}
tn_Area1_tabMaySept
tx_Area1_tabMaySept
```


## CONCLUSIONS

The 10-days time window tends to leave out several important events. On the other hand, the 7-days time window
may split a unique HW event into two. However, it is worth noticing that, for the period May-September, the number of events selected by the two type of time windows above the threshold of $300$ cells is very similar and the total number of  **tn**(**tx**) HW events sum up to $152$($137$)  and $137$($122$) for 7-days and 10-days, respectively. __My proposal is to take $300$ as minimum number of cells involved (spatial extension of the HW) and 7-days time window for cutting out dates of the same HW__.



